Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
major restructure; much to fix and transition

@@

@@

\section{General Lemmata}
First we present the general inductive lemmata that will be applied
for all genera.

@@

@@

\begin{rem}\label{rem:minimal_quadratic_trivial_case}
It will be useful to use lemma \ref{lem:minimal_quadratic} in the
case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space).  
\end{rem}

TRANSITION
\todo{transition!}

\ssec{Inductive Theorem: Increasing the Ramification Orders}
\label{ssec:g_0_ram_orders}
In this section, we aim to prove the inductive theorem, Theorem
~\ref{thm:ram_order_ind}. Under fairly general
conditions, this theorem will allow us to show that if Theorem ~\ref
{thm:ram_order_ind} holds for a curve with signature
$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.

@@

@@

\ssec{Main Theorem for Genus 1}

\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}

\end{lem}
\begin{proof}
Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
dimension counting, we see that 
\[
	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
\]
\[
	\langle y_1^a y_2: a\ge 0\rangle
\]
form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).

\begin{lem}\label{lem:adding_points_saturation_2_to_1_no_log}
Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_3^2
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}
\begin{proof}
The proof follows similarly to that of lemma 
\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
generator in degree 3 rather than degree 2.  
\end{proof}

@@

We have Lemma ~\ref{lem:minimal_quadratic}.
\todo{fill in hole here}

@@

Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
\todo{fill out}

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Inductive Lemmata %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Inductive Lemmata}
First we present the general inductive lemmata that will be applied
for all genera.
\todo{intro}

@@

\begin{rem}
Fact about quotient.
\end{rem}

@@

\begin{rem}
\label{rem:minimal_quadratic_trivial_case}
It will be useful to use lemma \ref{lem:minimal_quadratic} in the
case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$
are $k$-minimal generators for $I'$ (over the trivial base vector
space).  
\end{rem}

Transition words.
\todo{transition!}

\ssec{Inductive Lemmata: Adding Points}
\label{ssec:add_pts}
In this section, we prove various inductive statements about
generators and relations with respect to adding points.

\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

\begin{proof}
Since adding $P$ to $L'$, reduces saturation from 2 to 1, $h^0(X, \lfloor L \rfloor)=1$.  
Choose any $y_1\in H^0(X,\lfloor L\rfloor)$; we know by saturation arguments that $-
\ord_P(y_1)=1$.  Furthermore, since $\delta>0$, we use Riemann-Roch to deduce that for 
all $d>1$ $h^0(X,\lfloor dL\rfloor)=h^0(dL')+d$, so $(R_\halfcan)_d$ is a $d$ dimension $k
$-vector space over $(R_{\halfcan'})_d$.  In particular, this means we can generically 
choose an element $y_2\in H^0(X,\lfloor 2L\rfloor)$ linearly independent from $y_1^2$.  By 
dimension counting, we see that 
\[
	\langle y_1^a x_2^b x_3^c: a\ge 0, b\ge 0, c\in \{0,1\}\rangle
\]
\[
	\langle y_1^a y_2: a\ge 0\rangle
\]
form a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  This completes part (a).

\begin{lem}
\label{lem:adding_points_saturation_2_to_1_no_log}
Let $(\sx, 2P, \halfcan)$ and $(\sx, 0, L')$ be tame separably rooted log stacky spin curves 
with $P$ not in the support of $\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_
\tau; 2)$ and $(g; e_1, \ldots, e_\tau, 0)$ with $g\ge 2$ be their respective signatures.  
Suppose $sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose 
$R_{\halfcan'} = k[x_2, x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  
Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_3$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_3$ respectively, such that $-\ord_P(y_3)>1$ and $\{y_1^3, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_3]$ with $grlex$ so that $y_3 \prec y_1$ and equip $k[y_1, y_3, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_3, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_3 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_3^2
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}
\begin{proof}
The proof follows similarly to that of lemma 
\ref{lem:adding_points_saturation_2_to_1_with_log}, with the change that $(R_
\halfcan)_2$ is only a degree 1 $k$-vector space over $(R_{\halfcan'})_2$ forcing a 
generator in degree 3 rather than degree 2.  
\end{proof}

Transition to genus one.
\todo{transition!}

Transition words.
\todo{transition!}

\todo{do these corollaries fit here?}

Transition words.
\todo{transition!}

Transition words.
\todo{transition!}

\ssec{Inductive Lemma: Raising Ramification Orders}
\label{ssec:ram_orders}
In this section, we aim to prove the inductive theorem, Theorem
~\ref{thm:ram_order_ind}. Under fairly general
conditions, this theorem will allow us to show that if Theorem ~\ref
{thm:ram_order_ind} holds for a curve with signature
$(0;e_1',\ldots, e_r';0)$ then it also holds for a curve with
signature $(0;e_1,\ldots, e_r;0)$ with $e_i' - e_i \in \{0,2\}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% High genus %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus one %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\ssec{Main Theorem for Genus 1}
Words.

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Genus zero %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We have Lemma ~\ref{lem:minimal_quadratic}.
\todo{fill in hole here, with adding points too}

@@

\todo{transition}
Here we describe induction of raising degrees from Theorem ~\ref{thm:ram_order_ind}
\todo{fill out}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Acknowledgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
